Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-06 Paper.tex
Added a ref. for Moore's Law: THOMPSON200620.

Note that \mindifficulty is the difficulty of the genesis block. The effect of the difficulty parameter \homesteadmod on a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. \expdiffsymb results in the difficulty increasing every 10000 blocks, which also stabilises the time difference between blocks, as computation power becomes more efficient, \eg with Moore's Law (\cite{Multichain}, \cite{Moore}).

>>>>

Note that \mindifficulty is the difficulty of the genesis block. The effect of the difficulty parameter \homesteadmod on a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. \expdiffsymb results in the difficulty increasing every 10000 blocks, which also stabilises the time difference between blocks, as computation power becomes more efficient, \eg with Moore's Law (\cite{Multichain}, \cite{THOMPSON200620}).
